\sysfull

### 2019-06-24 paper/TOSN/response-letter/responseLetter.tex

\newcommand{\referee}[1]{
	{\item \color{OliveGreen} \emph{{#1}}}
	\label{R\therefereeCounter:\arabic{enumi}}
}

\definecolor{OliveGreen}{rgb}{0.1,0.2,0.5}

\newcommand{\response}[1]{{\color{blue} #1}}

\newenvironment{additionalQuestions}{%
\textbf{\large Additional questions}
\begin{enumerate}%
\renewcommand{\labelenumi}{\textbf{[Q:\,\arabic{enumi}]}} %
}{\end{enumerate}}

\newenvironment{editor}{%
\textbf{\large Additional remarks}
\begin{enumerate}%
\renewcommand{\labelenumi}{\textbf{[R:\,\arabic{enumi}]}} %
}{\end{enumerate}}

@@

\newcounter{refereeCounter}

\newenvironment{responses}{%
\refstepcounter{refereeCounter}%
\textbf{\large Comments by Referee \therefereeCounter}
\begin{enumerate}%
\renewcommand{\labelenumi}{\textbf{[C:\,\arabic{enumi}]}} %
}{\end{enumerate}}

@@

\textbf{TOSN-2019-0002:} {\sl Coala: Dynamic Task-Based Intermittent Execution for Energy-Harvesting Devices}

\bigskip

Dear Editor,\\

We would like to thank for handling our submission and providing valuable review results. 
We are also grateful to the reviewers for their substantial effort spent for evaluating our work. \\

@@

\pagebreak

\begin{responses}

\referee{In section 2.3, authors mention "these models do not rely on capturing an expensive checkpoint, they are usually faster than the checkpoint-based solution [12, 42]". I don't fully agree with this. It depends on the underlying checkpointing mechanism. If it copies complete stack every time during the checkpoint then yes it's expensive. But checkpointing mechanism like incremental checkpointing [2] (also see the paper by Faycal Ait Aouda), where you only update modified variables, is much better in terms of energy consumption (even better than the task-based solution in my opinion). Also, [12] and [42] are not checkpoint-based solutions.}

\response{As indicated by the reviewer, [12, 42] are not checkpoint systems. They are task-based systems and their results show that task-based systems are faster than checkpoint-based ones. Therefore, we restated their claim and provided the supporting references, which are [12, 42].\\
 Coala addresses deficiencies in the \emph{static} task-based systems and provides more efficient alternative. Therefore, we compared its performance against the state-of-the-art task-based runtime.}

@@

\referee{In section 7.1, authors mention "produce a high number of complete runs". Please mention the exact number iterations. Also please mention the capacitor size for the WIPS 5.1.}

\response{The number of complete runs, which ranges between 4 and 125, and WISP capacitor size are added to Section 7.1.}

@@

\referee{In figure 10, it is not very clear how authors normalized the values for Coala in case of fft for 30cm and 50cm. Also in the text authors state that "This is marked with $\infty$ signs in Fig. 9", its figure 10. }

\response{We normalized these two special cases on 1 second. This infromation is added to Section 8.2; additionally, the figure reference is corrected. }

@@

\referee{However, I was hoping to see more evaluations to understand the effect of capacitor size. In the introduction, authors state that "Coala is the only system that eliminates restructuring and re-compilation of applications considering device’s energy buffer". However, in the evaluation, I didn't find any graph related to the performance of Coala w.r.t to different capacitor sizes.}

\response{An additional experiment regarding the capacitor size has been conducted and the results are added to Section 8.2.}

\referee{I would have also liked to see a comparison between Coala and Region Formation [2]. Both try to reduce checkpointing overhead.}

\response{As it is indicated in response \hyperref[R:1]{[R:1]}, Coala addresses deficiencies in the \emph{static} task-based systems and provides a more efficient alternative. Therefore, we compared its performance against the performance of the state-of-the-art task-based runtime.}

\referee{Also, I would suggest incorporating error bars in all the graphs as your "results were averaged across the duration of the experiment"}

\response{We chose to normalize the results to focus on the speedup (or slowing down) and that is why we omitted the error-bars.}

\referee{In the abstract (and also in the introduction), authors claim that "Coala reduces run time by up to 54\%", however, I didn't see this number again anywhere in the evaluation.}

\response{This number is highlighted in Section 8.2.}

\referee{mwntioned typos}

\response{These typos are corrected.}

@@

\end{responses}

\begin{additionalQuestions}
\referee{Does this paper cite and use appropriate references?: No\\
If not, what important references are missing?: 
Ratchet and Clank were the first to propose using a timer for breaking up a long task so that it can make forward progress during short power cycles.  The authors propose the idea as if they were the first to use it.}

\response{In section 4.2, we explicitly mentioned that the timer-based approach is similar to [72]. [72] references the Ratchet paper. Table 1 mentioned Ratchet and Clank by names and they are referenced in our original paper.}
\end{additionalQuestions}

\begin{editor}
\referee{}
\response{We have added a new figure to the paper, i.e. Fig. 5. The figure's sole purpose is to aid explaining the concept of \textit{task coalescing}.
We hope that this modification further helps in understanding the core contribution of our paper.}
\end{editor}

### 2019-06-24 paper/TOSN/background.tex
center figure and add label
minor revision TOSN
First iteration

% Table
\begin{table}%
\caption{Simulation Configuration}
\label{tab:one}
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{ll}
  \toprule
        Model & Data Copied to/from NVRAM \\
        \hline
        Mementos~\cite{mementos}    & Registers + Stack     \\
        DINO~\cite{dino}    & Registers + Stack + WAR NV variables \\%used in task\\
        Chain~\cite{chain}  & PC + NV variables used in task\\
        Alpaca~\cite{alpaca}    & PC + WAR NV variables used in task\\
        Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
        Region Formation~\cite{baghsorkhi_cgo_2018} & Registers + Updated variables in task \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}
  \label{table:chechpoint_comparison}
\end{table}%

@@

Software running on an energy-harvesting device executes {\em intermittently} because power sources are not always available to harvest and buffer sufficient operational energy. An intermittent execution is composed of operating periods interspersed with power failures~\cite{dino,chain,alpaca,ratchet}. The frequency of failures depends on the size of the device's energy storage buffer (a larger buffer allows longer operating periods), current consumption and incoming energy.

\begin{figure}
	\begin{subfigure}{0.4\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{figures/war-example.pdf}
		\caption{WAR-affected code}
		\label{fig:war-example}
	\end{subfigure}
	\begin{subfigure}{0.4\columnwidth}
		\centering
		\includegraphics[width=\columnwidth]{figures/war-execution.pdf}
		\caption{WAR-affected execution}
		\label{fig:war-execution}
	\end{subfigure}
	\caption{WAR dependency example. \texttt{NV} marks non-volatile variables, \texttt{checkpoint()} is a checkpoint of volatile state.	\label{fig:w-a-r}}
\end{figure}

A power failure clears volatile state (e.g., registers and SRAM) while non-volatile memory (e.g., FRAM) persists. Upon a power failure, control flows to a prior point in the execution: by default, to the beginning of {\tt main()}. Early intermittent systems preserved progress by periodically checkpointing volatile execution context to non-volatile memory~\cite{mementos}, sometimes requiring hardware support~\cite{mottola2017harvos,hibernusplusplus,hibernus,idetic,quickrecall}, Table~\ref{table:chechpoint_comparison} summarizes the data that gets copied to and from the non-volatile memory in service of memory consistency and progress preservation. Checkpointing volatile state alone does not ensure data consistency when the system can directly manipulate non-volatile memory~\cite{mspcdino}. Precisely, data can get inconsistent when code includes a \emph{write-after-read} (WAR) dependency between operations that manipulate non-volatile memory. Fig.~\ref{fig:w-a-r} illustrates how state can become inconsistent in an intermittent execution using a simple example of an average operation over an array of integers.
The non-volatile variable \texttt{sum} introduces the WAR, being read and written sequentially by the increment operation. If a power failure occurs right before updating the non-volatile index \texttt{i} (Fig.~\ref{fig:war-execution}, Line 6), \texttt{sum} gets erroneously incremented twice consecutively by the same array element (Fig.~\ref{fig:war-execution}, Lines 5 and 8).

>>>>

% Table
\begin{table}%
\caption{Simulation Configuration}
\label{tab:one}
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{ll}
  \toprule
        \textbf{Model} & \textbf{Data Copied to/from NVRAM} \\
        \hline
        Mementos~\cite{mementos}    & Registers + Stack     \\
        DINO~\cite{dino}    & Registers + Stack + WAR NV variables \\%used in task\\
        Chain~\cite{chain}  & PC + NV variables used in task\\
        Alpaca~\cite{alpaca}    & PC + WAR NV variables used in task\\
        Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
        Region Formation~\cite{baghsorkhi_cgo_2018} & Registers + Updated variables in task \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}
  \label{table:chechpoint_comparison}
\end{table}%

@@

Software running on an energy-harvesting device executes {\em intermittently} because power sources are not always available to harvest and buffer sufficient operational energy. An intermittent execution is composed of operating periods interspersed with power failures~\cite{dino,chain,alpaca,ratchet}. The frequency of failures depends on the size of the device's energy storage buffer (a larger buffer allows longer operating periods), current consumption and incoming power.

\begin{figure}		
	\centering
	\begin{minipage}{.8\textwidth}
	\begin{subfigure}{.5\columnwidth}
			\includegraphics[width=\columnwidth, trim={.3cm 0 0 0}]{figures/war-example.pdf}
		\caption{WAR-affected code}
		\label{fig:war-example}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
			\includegraphics[width=\columnwidth,trim={.3cm 0 0 0 }  ]{figures/war-execution.pdf}
		\caption{WAR-affected execution}
		\label{fig:war-execution}
	\end{subfigure}
	\caption{WAR dependency example. \texttt{NV} marks non-volatile variables, \texttt{checkpoint()} is a checkpoint of volatile state.	\label{fig:w-a-r}}
	\end{minipage}
\end{figure}

A power failure clears volatile state (e.g., registers and SRAM) while non-volatile memory (e.g., FRAM) persists. Upon a power failure, control flows to a prior point in the execution: by default, to the beginning of {\tt main()}. Early intermittent systems preserved progress by periodically checkpointing volatile execution context to non-volatile memory~\cite{mementos}, sometimes requiring hardware support~\cite{mottola2017harvos,hibernusplusplus,hibernus,idetic,quickrecall}, Table~\ref{table:chechpoint_comparison} summarizes the data that get copied to and from the non-volatile memory in service of memory consistency and progress preservation. Checkpointing volatile state alone does not ensure data consistency when the system can directly manipulate non-volatile memory~\cite{mspcdino}. Precisely, data can get inconsistent when code includes a \emph{write-after-read} (WAR) dependency between operations that manipulate non-volatile memory. Fig.~\ref{fig:w-a-r} illustrates how state can become inconsistent in an intermittent execution using a simple example of an average operation over an array of integers.
The non-volatile variable \texttt{sum} introduces the WAR, being read and written sequentially by the increment operation. If a power failure occurs right before updating the non-volatile index \texttt{i} (Fig.~\ref{fig:war-execution}, Line 6), \texttt{sum} gets erroneously incremented twice consecutively by the same array element (Fig.~\ref{fig:war-execution}, Lines 5 and 8).

### 2019-06-24 paper/TOSN/coalescing.tex
First iteration

{\em Energy-oblivious} (EO) coalescing strategy treats all tasks as having unity weight and varies the size of the coalescing target linearly. In such a scheme, the number of tasks to coalesce, $C$, increases by a constant $x$ when a coalesced sequence of tasks commits, and decreases by the same constant $x$ when a coalesced sequence of tasks fails to complete, i.e., after a power failure. The characteristic operations of EO are
%
\begin{equation}
	\begin{split}
		f_\text{reboot}(C) & = C - x, \\
		f_\text{weight}(T_\text{i}) & =  1, \\
		f_\text{commit}(C) & = C + x.
	\end{split}
	\label{eq:eo}
\end{equation}
%
EO reacts slowly to the variation in the energy required to execute different tasks and to the variation in the effective quantum of energy available to the device. With the successful commit of each coalesced task sequence, $C$ increases. Eventually, the target may be too high and only a coalesced task composed of a few units will commit without interruption by a power failure. The strategy then linearly decreases $C$, eventually reaching a value that allows completion. A key limitation of this algorithm lies in the equality of the target decrease in $f_\text{reboot}$ and the increase in $f_\text{commit}$. Let us assume $x=1$. If, after $k$ successful commits, the target must decrease to its original value $C-k$ due to an energy drop, EO requires $k$ successive power failures, before being able to progress.

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{figures/dif_cap}
    \caption{\add{Anatomy of \sys coalescing---A snapshot of measured data showing how \sys coalesces static tasks. \sys takes advantage of the guarantee that an energy buffer offers after a reboot: code execution resumes after energy accumulation reaches the operational threshold (a maximum threshold). Thus, \sys starts with a big coalesced task and shrinks it gradually as the risk of a power failure increases.}}
    \label{fig:coal_anatomy}
\end{figure}

@@

\add{
Fig.~\ref{fig:coal_anatomy} shows \sys in action. It shows how \sys coalesces aggressively when the execution is just re-started, taking advantage of the full energy buffer, and how it reduces the coalesced task gradually to minimize the risk of significant progress loss when the device fails. The average measured static task size is $\approx$\,0.28 $ms$ while the commit time (time needed to save the data into the non-volatile memory) averages at  $\approx$\,0.64 $ms$. This highlights the importance of coalescing.
}

>>>>

{\em Energy-oblivious} (EO) coalescing strategy treats all tasks as having unity weight and varies the size of the coalescing target linearly. In such a scheme, the number of tasks to coalesce, $C$, increases by a constant $x$ when a coalesced sequence of tasks commits and decreases by the same constant $x$ when a coalesced sequence of tasks fails to complete, i.e., after a power failure. The characteristic operations of EO are
%
\begin{equation}
	\begin{split}
		f_\text{reboot}(C) & = C - x, \\
		f_\text{weight}(T_\text{i}) & =  1, \\
		f_\text{commit}(C) & = C + x.
	\end{split}
	\label{eq:eo}
\end{equation}
%
EO reacts slowly to the variation in the energy required to execute different tasks and to the variation in the effective quantum of energy available to the device. With the successful commit of each coalesced task sequence, $C$ increases. Eventually, the target may be too high and only a coalesced task composed of a few units will commit without interruption by a power failure. The strategy then linearly decreases $C$, eventually reaching a value that allows completion. A key limitation of this algorithm lies in the equality of the target decrease in $f_\text{reboot}$ and the increase in $f_\text{commit}$. Let us assume $x=1$. If, after $k$ successful commits, the target must decrease to its original value $C-k$ due to an energy drop, EO requires $k$ successive power failures, before being able to progress.

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{figures/dif_cap}
    \caption{\add{Anatomy of \sys coalescing---A snapshot of measured data showing how \sys coalesces static tasks. \sys takes advantage of the guarantee that an energy buffer offers after a reboot: code execution resumes after energy accumulation reaches the operational threshold (a maximum threshold). Thus, \sys starts with a big coalesced task and shrinks it gradually as the risk of a power failure increases. T stands for task code execution and C for commit or power cut.}}
    \label{fig:coal_anatomy}
\end{figure}

@@

\add{
Fig.~\ref{fig:coal_anatomy} shows a real measurement of \sys coalesced tasks. It shows how \sys coalesces aggressively when the execution is just re-started, taking advantage of the full energy buffer, and how it reduces the coalesced task gradually to minimize the risk of significant progress loss when the device fails. The average measured static task size is $\approx$\,0.28\,ms while the commit time (time needed to save the data into the non-volatile memory) averages at  $\approx$\,0.64\,ms. This highlights the importance of coalescing.
}

### 2019-06-24 paper/TOSN/evaluation.tex
First iteration

% \end{wrapfigure}
%
%Building on top of the existing work, we have selected the most efficient task-based run-time library~\cite{alpaca} and compared \sys against it.
Our evaluation quantitatively demonstrates that \sys (i) \emph{reduces memory
protection overhead}, (ii) \emph{improves execution speed} in most cases,
and (iii) \emph{is able to progress} where static systems suffer from a task non-termination loop. 
%
\subsection{Characterization of Overhead}
\label{sec:coala_overhead}

@@

\paragraph{Protected Memory Accesses Breakdown.}
%
Fig.~\ref{fig:mem-accesses} breaks down protected memory accesses
into three categories.
%
Each type of protected access incurs a different.
Accessing the most recently used SRAM page is of the cheapest kind.
Accessing a different page in SRAM has a slightly higher cost.
Finally, accessing a page that needs to be swapped in
from FRAM into SRAM is the most expensive.
%
The results in the figure show that the overwhelming majority of accesses are
of the cheapest kind, which motivated us to optimize this accesses in our
implementation.
%
Only \textit{cuckoo}, \textit{dijkstra}, and \textit{fft} have non-negligible
number of accesses to a different SRAM page, which is due to the larger working
set and a less regular access pattern in these applications.
%
In general, memory access patterns are shaped by the application, and the more
program state is protected, the higher the rate of page swaps.
%
\subsection{Execution Time}
\label{sec:result_coalescing}
%
Having shown in Section~\ref{sec:coala_overhead} that coalescing reduces
overhead, we now investigate the outcome of this reduction on the total
execution time. We first investigate different variants of \sys and
then compare the best variant to Alpaca~\cite{alpaca}.

@@

\caption{\add{Comparison of \sys performance on two different capacitor sizes. We see that \sys optimizes its coalesced task size based on the energy buffer size.
\textbf{coalesced task} refers to the first coalesced task after a reboot, \textbf{exp. time} shows the experiment duration, and the \textbf{runs} column lists 
the number of complete runs of the \textit{sort} application during the experiments.}
}
\label{tab:dif_cap}
\add{
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llllll}
  \toprule
    \textbf{cap. size} ($\mu\text{f}$)& \textbf{exp. time} ($s$)& \textbf{duty cycle} & \textbf{coalesced task} ($ms$)   & \textbf{runs} & \textbf{app run-time} ($ms$) \\
        \hline
    47                 &1205             & 12.93\%    & 33                        & 85       & 183      \\
    470                &1205             & 12.79\%    & 88                        & 87       & 177 \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}  
}
\end{table}%

Fig.~\ref{fig:coalescing} shows \sys's run time of two coalescing
strategies (EG, WEG) normalized to the run time without coalescing (NC).
%
The results show that all benchmarks
complete faster with coalescing than without coalescing: from 25\%
(\textit{ar}) up to 70\% (\textit{sort}).
%
This speedup is a consequence of the reduced overhead demonstrated in
Section~\ref{sec:coala_overhead}.
%
However, the magnitude of the speedup is (1) highly application-dependent and
(2) largely similar across the two coalescing strategies, with the exception of
\textit{fft}.
%
In some cases (\textit{bc}, \textit{cuckoo}, \textit{sort}) WEG's task weighting
system is counter-productive.
%
This occurs in task decompositions with energy-uniform tasks, where counting
tasks disregarding their energy consumption provides an equal amount of information
with a smaller effort.
%
In \textit{fft}, tasks are not uniform, and accounting for their different weights
beneficial. In fact, the lack of task energy awareness is detrimental: with EG
\textit{fft} runs slower than without any coalescing (NC).
%
The speedup is highest for \textit{bc}, \textit{cuckoo}, \textit{dijkstra} and
\textit{sort}, because their tasks are relatively small and are easily coalesced.
%

@@

\paragraph{\add{Different Capacitor Sizes}}
\add{
Table~\ref{tab:dif_cap} shows how \sys optimizes its Coalescing task size based on the amount of buffered energy.
We see that \sys scales up its coalesced task size with a bigger energy buffer and vise versa. This allows it to reduce the time-to-completion of the applications. For example, 
the \textit{sort} run-time is reduced from 183\,$ms$ to 177\,$ms$ when the capacitor is changed from 47\,$\mu$f to 470\,$\mu$f. It should be emphasized that a device with a bigger energy buffer suffers less from power failures (but requires longer charging time). However, as has been measured in Fig.~\ref{fig:overallOverheadBreakdown} and explained in Fig.~\ref{fig:coal_anatomy}, the re-execution penalty for the \textit{sort} application is negligible.  
}

\paragraph{Benefits of Adaptive Tasks.}
%
We now compare \sys's performance to Alpaca~\cite{alpaca}---a
\emph{non-adaptive} task-based system with tasks fixed at compile-time.
Fig.~\ref{fig:runtime} shows the average execution time of each
application for \sys and Alpaca, \add{normalized to the latter or, when not possible, to one second}.
\sys provides a performance benefit compared to Alpaca for most
applications. \add{For example, it is 54\% faster than Alpaca when executing the \textit{sort} application. In general,}  the speedup is greatest for applications with repeated WAR
dependencies throughout their code, particularly involving arrays
(\textit{dijkstra}, \textit{fft} and \textit{sort}). \sys's VMM
successfully amortizes the overhead of protecting memory that is accessed in
such patterns.  In applications without locality among accesses to protected
variables, including array elements, \sys incurs overhead from memory
virtualization that causes its performance to be comparable to (or worse than)
Alpaca (\textit{ar}, \textit{cuckoo}).

Due to its static progressing behavior, Alpaca was unable to complete the \textit{fft} benchmark on distances larger than 15\,cm\footnote{At distances greater than 15\,cm, energy incoming during
execution is negligible and stored energy is insufficient to complete some of
the static tasks.}. This is marked with $\infty$ signs in Fig.~\ref{fig:runtime}. \sys, however, managed to complete \textit{fft} by enabling its task downscaling at 30\,cm and 50\,cm from the energy source.

>>>>

Our evaluation quantitatively demonstrates that \sys (i) \emph{reduces memory
protection overhead}, (ii) \emph{improves execution speed} in most cases,
and (iii) \emph{is able to progress} where static systems suffer from a task non-termination loop. 
%
\subsection{Characterization of Overhead}
\label{sec:coala_overhead}

@@

\paragraph{Protected Memory Accesses Breakdown.}
%
Fig.~\ref{fig:mem-accesses} breaks down protected memory accesses
into three categories.
%
Each type of protected access incurs a different overhead.
Accessing the most recently used SRAM page is of the cheapest kind.
Accessing a different page in SRAM has a slightly higher cost.
Finally, accessing a page that needs to be swapped in
from FRAM into SRAM is the most expensive.
%
The results in the figure show that the overwhelming majority of accesses are
of the cheapest kind, which motivated us to optimize this accesses in our
implementation.
%
Only \textit{cuckoo}, \textit{dijkstra}, and \textit{fft} have non-negligible
number of accesses to a different SRAM page, which is due to the larger working
set and a less regular access pattern in these applications.
%
In general, memory access patterns are shaped by the application, and the more
program state is protected, the higher the rate of page swaps.
%
\subsection{Execution Time}
\label{sec:result_coalescing}
%
Having shown in Section~\ref{sec:coala_overhead} that coalescing reduces
overhead, we now investigate the outcome of this reduction on the total
execution time. We first investigate different variants of \sys and
then compare the best variant to Alpaca~\cite{alpaca}. Additionally, we compare \sys
performance running with different energy buffer sizes.

@@

\caption{\add{Comparison of \sys performance on two different capacitor sizes using the \textit{sort} application. We see that \sys optimizes its coalesced task size based on the energy buffer size.
\textbf{Coalesced task} refers to the first coalesced task after a reboot, \textbf{Exp. time} shows the experiment duration, the \textbf{Runs} column lists the number of complete runs of the application during the experiments. \textbf{Run time} is the device collective uptime needed to finish a single iteration of the \textit{sort} application.}
}
\label{tab:dif_cap}
\add{
\begin{minipage}{\columnwidth}
\begin{center}
\begin{tabular}{llllll}
  \toprule
    \textbf{Cap. size} ($\mu\text{f}$)& \textbf{Exp. time} ($s$)& \textbf{Duty cycle} & \textbf{Coalesced task} ($ms$)   & \textbf{Runs} & \textbf{Run time} ($ms$) \\
        \hline
    47                 &1205             & 12.93\%    & 33                        & 85       & 183      \\
    470                &1205             & 12.79\%    & 88                        & 87       & 177 \\
  \bottomrule
\end{tabular}
\end{center}
\end{minipage}  
}
\end{table}%

Fig.~\ref{fig:coalescing} shows \sys's run time of two coalescing
strategies (EG, WEG) normalized to the run time without coalescing (NC).
%
The results show that all benchmarks
complete faster with coalescing than without coalescing: from 25\%
(\textit{ar}) up to 70\% (\textit{sort}).
%
This speedup is a consequence of the reduced overhead demonstrated in
Section~\ref{sec:coala_overhead}.
%
However, the magnitude of the speedup is (1) highly application-dependent and
(2) largely similar across the two coalescing strategies, with the exception of
\textit{fft}.
%
In some cases (\textit{bc}, \textit{cuckoo}, \textit{sort}) WEG's task weighting
system is counter-productive.
%
This occurs in task decompositions with energy-uniform tasks, where counting
tasks disregarding their energy consumption provides an equal amount of information
with a smaller effort.
%
In \textit{fft}, tasks are not uniform, and accounting for their different weights is
beneficial. In fact, the lack of task energy awareness is detrimental: with EG
\textit{fft} runs slower than without any coalescing (NC).
%
The speedup is highest for \textit{bc}, \textit{cuckoo}, \textit{dijkstra} and
\textit{sort}, because their tasks are relatively small and are easily coalesced.
%

@@

\paragraph{Benefits of Adaptive Tasks.}
%
We now compare \sys's performance to Alpaca~\cite{alpaca}---a
\emph{non-adaptive} task-based system with tasks fixed at compile-time.
Fig.~\ref{fig:runtime} shows the average execution time of each
application for \sys and Alpaca, \add{normalized to the latter or, when not possible, to one second}.
\sys provides a performance benefit compared to Alpaca for most
applications. \add{For example, it is 54\% faster than Alpaca when executing the \textit{sort} application. In general,}  the speedup is greatest for applications with repeated WAR
dependencies throughout their code, particularly involving arrays
(\textit{dijkstra}, \textit{fft} and \textit{sort}). \sys's VMM
successfully amortizes the overhead of protecting memory that is accessed in
such patterns.  In applications without locality among accesses to protected
variables \sys incurs overhead from memory
virtualization that causes its performance to be comparable to (or worse than)
Alpaca (\textit{ar}, \textit{cuckoo}).

Due to its static progressing behavior, Alpaca was unable to complete the \textit{fft} benchmark on distances larger than 15\,cm\footnote{At distances greater than 15\,cm, energy incoming during
execution is negligible and the stored energy is insufficient to complete some of
the static tasks.}. This is marked with $\infty$ signs in Fig.~\ref{fig:runtime}. \sys, however, managed to complete \textit{fft} by enabling its task downscaling at 30\,cm and 50\,cm from the energy source.

\paragraph{\add{Different Capacitor Sizes}}
\add{
Table~\ref{tab:dif_cap} shows how \sys optimizes its Coalescing task size based on the amount of buffered energy.
We see that \sys scales up its coalesced task size with a bigger energy buffer and vice versa. This allows it to reduce the time-to-completion of the applications. For example, 
the \textit{sort} run-time is reduced from 183\,ms to 177\,ms when the capacitor is changed from 47\,$\mu$F to 470\,$\mu$F. It should be emphasized that a device with a bigger energy buffer suffers less from power failures (but requires longer charging time). However, as has been measured in Fig.~\ref{fig:overallOverheadBreakdown} and explained in Fig.~\ref{fig:coal_anatomy}, the re-execution penalty for the \textit{sort} application is negligible.  
}
